Artificial ecosystem selection to deduce the mapping between microbial community structure and ecosystem function

### 2020-10-15 Manuscript/manuscript.Rmd
move model out of manuscript.Rmd, update makefile

```{r dev_model}
fluxes <- read_tsv('../Output/fluxes.tsv')
deviance <-
  fluxes %>% 
  select(treat, passage, estimate) %>% 
  group_by(passage, treat) %>% 
  summarize(mean = mean(estimate), .groups = "drop") %>% 
  pivot_wider(names_from = treat, values_from = mean) %>% 
  mutate(deviance = p - n)

se <- function(x, na.rm = FALSE){
  sqrt(var(if (is.vector(x) || is.factor(x)) x else as.double(x), 
    na.rm = na.rm)) / sqrt(length(if (na.rm == TRUE) na.omit(x) else x))
}

sed <- function(p, n, na.rm = FALSE) {
  sqrt(se(p, na.rm = na.rm) ^ 2 + se(n, na.rm = na.rm)^ 2)
}

deviance$se <-
  fluxes %>% 
  select(treat, passage, estimate) %>% 
  mutate(x = 1:nrow(fluxes)) %>% 
  pivot_wider(names_from = treat, values_from = estimate) %>% 
  group_by(passage) %>% 
  summarize(sed = sed(p, n, na.rm = TRUE), .groups = "drop") %>% 
  pull(sed)

dev_fit <- rma(deviance~passage, se^2, method="FE", data = deviance)

@@

dev_pred <- predict(dev_fit)
```

@@

```{r dev_fig, fig.width=4, fig.height=3, fig.cap=figures("deviance")}
passages <- length(deviance$passage)
ggplot(deviance, aes(x = passage, y = deviance, ymin = deviance - se, ymax = deviance + se)) + 
  geom_ribbon(aes(ymin = dev_pred$ci.lb, ymax = dev_pred$ci.ub), alpha = 0.2) +
  geom_pointrange(color = 'darkorange2') + 
      geom_segment(aes(x = 1, xend = passages, y = dev_fit$beta[1] + dev_fit$beta[2], yend = dev_fit$beta[1] + dev_fit$beta[2]*passages), color = 'darkorange2', size = 1) +
  labs(x = "Passage Number", y = "Deviation from Control (P - N)")+
  theme_bw()

ggsave('new_select_fig.pdf', width = 4, height = 3)

>>>>

```{r dev_model}
fluxes <- read_tsv('../Output/fluxes.tsv')
deviance <- read_tsv('../Output/deviance.tsv')
rma_output <- readRDS('../Output/response.rds')
dev_fit <- readRDS('../Output/dev_fit.rds')
dev_pred <- predict(dev_fit)

@@

passages <- length(deviance$passage)

@@

```{r dev_fig, fig.width=4, fig.height=3, fig.cap=figures("deviance")}
ggplot(deviance, aes(x = passage, y = deviance, ymin = deviance - se, ymax = deviance + se)) + 
  geom_ribbon(aes(ymin = dev_pred$ci.lb, ymax = dev_pred$ci.ub), alpha = 0.2) +
  geom_pointrange(color = 'darkorange2') + 
      geom_segment(aes(x = 1, xend = passages, y = dev_fit$beta[1] + dev_fit$beta[2], yend = dev_fit$beta[1] + dev_fit$beta[2]*passages), color = 'darkorange2', size = 1) +
  labs(x = "Passage Number", y = "Deviation from Control (P - N)")+
  theme_bw()
